Approximate Code: A Cost-Effective Erasure Code for Video Applications in Cloud Storage Systems

### 2019-04-08 ApproximateCode.tex
version2.1.2

@@

Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage module is necessary to preprocess the data. In our design, the middle layer performs automatic data identification and data distribution. It also implement \emph{I-Phase} in the encoding process and approximate recovery mode in the decoding process.

@@

\section{Evaluation}\label{evaluation}
In our evaluation, we first compare the approximate code with the RS code and some XOR-based code to demonstrate the performance benefits of our solution. Since 3DFTS is a typical erase code configuration, we use it as a baseline and set the minimum fault tolerance of important data to 3 ($ m + s \geqslant 3 $). We will then demonstrate the quality loss of multimedia data under the traditional and approximate recovery models of severe disk failure to assess the benefits of our approximate storage scheme. We use mathematical analysis and experiments to prove the effectiveness of the approximation code.

@@

\subsection{Evaluation methodology}

>>>>

\begin{table}[]
\begin{tabular}{|c|l|}
\hline
Symbols & Description                          \\ \hline\hline
$n$     & the number of chunks in a stripe     \\ \hline
$m$     & the number of parity chunks          \\ \hline
$r$     & the number of sectors in a chunk     \\ \hline
$s$     & the number of columns of $D_I$       \\ \hline
$t$     & the number of rows of $D_I$          \\ \hline
$D_I$   & the zone of important data sectors   \\ \hline
$D_M$   & the zone of minor data sectors       \\ \hline
$Q$     & the zone of important parity sectors \\ \hline
$P$     & the zone of minor parity sectors     \\ \hline
\end{tabular}
\end{table}

@@

Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage system is necessary to preprocess the data. In our design, the middle layer performs automatic data identification and data distribution. It also implement \emph{I-Phase} in the encoding process and approximate recovery mode in the decoding process.

@@

\section{Evaluation}\label{evaluation}
This section introduces a series of experiments we have conducted to verify the efficiendy of the Approximate Code.

@@

\subsection{Evaluation methodology}
In our evaluation, we first compare the Approximate Code with the RS code and some XOR-based codes to demonstrate the performance benefits of our solution. Since 3DFTS is a typical erasure code configuration, we use it as a baseline and set the minimum fault tolerance of important data to 3 ($ m + s \geqslant 3 $). We will then demonstrate the quality loss of multimedia data under the traditional and approximate recovery models of severe disk failure to assess the benefits of our approximate storage scheme. We use mathematical analysis and experiments to prove the effectiveness of the Approximate Code.
